%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, letterpaper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-darknight}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
\definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile}
\name{Bolívar}{Aponte Rolón}

\position{Ph.D.~candidate}
\address{Department of Ecology and Evolutionary Biology \textbar{}
Tulane University, New Orleans, LA 70118}

\mobile{+1-787-433-6970}
\email{\href{mailto:apontebolivar@gmail.com}{\nolinkurl{apontebolivar@gmail.com}}}
\github{bolivaraponte}
\twitter{bolaponte}
%\dateofbirth{January 1st, 1970}
%\homepage{www.posquit0.com}
%\linkedin{posquit0}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \hackerrank{hackerrank-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

%\quote{I am a curiosity driven community ecologist focused on plant-fungal symbiosis and genomics.}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Funga PBC}
  {1612 Canterbury Street\\ Austin, TX 78702}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Application for: Ecological Data Scientist}
% How the letter is opened
\letteropening{Head of Data Science and Hiring committee,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
    {Bolívar Aponte Rolón~~~·~~~Curriculum Vitae}{}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}
%\setlength{\parindent}{0.5cm}
\indent I am delighted to apply for the position of Ecology Data Scientist at Funga.  My name is Bolívar Aponte Rolón, and I am a PhD student in the Van Bael Lab at Tulane University. I am an ecologist with a keen interest in utilizing genomic data to address questions related to microbial community ecology, particularly focusing on symbiotic fungi in plants.

\indent During my Master's I asked how sustainable agriculture can host high levels of ant biodiversity and applied standard forest ecology practices (e.g. DBH, leaf litter biomass measures, soil core sampling) to asses how shade tree species in a 45 hectare plot in an organic coffee farms in Mexico can contribute to the biodiversity we see leaf litter ant colonies. My focus to smaller entities, specifically fungi and microbes, prompting my pursuit of a PhD.

\indent For my dissertation, I seek to understand the role of leaf functional traits and their impact on foliar fungal endophytes—symbiotic fungi residing inside leaves—in both tropical and alpine ecosystems. In the tropics, I explore how endophytes assemble in tropical trees under the influence of environmental filters imposed by leaf functional traits. I investigate how the acquired fungal community within host leaves influences the host's response to herbivory and pathogen damage. My subsequent research projects in alpine ecosystems in the Sierra Nevada involve studying endophytes in yellow monkey-flowers. My methodologies include field surveys and reciprocal transplant experiments to decipher the endophytes in yellow monkey-flowers and identify associated genes.

\indent Through my research projects I have honed strong analytical skills applied to genomic and ecological data sets. I have designed experiments that collect environmental data and biological samples for metagenomic analyses. To achieve this I have extracted DNA from leaf tissue of tropical trees and yellow monkeyflowers and prepared fungal amplicon libraries for high throughput sequencing. I use open-source and reproducible bioinformatic pipelines (i.e. DADA2) and tools (e.g. cutadapt, Trimmomatic) in \emph{R} and Python programming languages to explore creatively the underpinnings of fungal communities and their correlations with the environment. For this I use general linear mixed models and ordination techniques to understand plant-fungal symbioses.  My proficiency in statistics coupled with my hands-on experience in field biology positions me as a valuable asset to Funga's objective of comprehending treatment effect sizes and correlations in inoculation experiments. I am well-equipped to contribute to the development of innovative strategies for sustainable forestry practices.

\indent In addition, I have developed strong communication and teams skills as a Product Developer for the Connolly Alexander Institute for Data Science at Tulane University. I collaborate in a team designing and employing data literacy workshops, impacting ~ 20 participants per instance. In this capacity I bridge the technical side of data science and communicate with our stakeholders to ensure the team's objectives and products meet the organizational needs. 

\indent Thank you for considering my application. I am excited about the prospect of contributing to Funga's impactful work, and I look forward to the possibility of discussing how my skills align with your team's vision.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
