%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Bolívar}{Aponte Rolón}

\position{Ph.D.~candidate}
\address{3033 Chippewa St.~\textbar{} New Orleans, LA 70115}

\mobile{+1-787-433-6970}
\email{\href{mailto:apontebolivar@gmail.com}{\nolinkurl{apontebolivar@gmail.com}}}
\github{bolivaraponte}
\twitter{bolaponte}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}

\quote{I am curiosity driven community ecologist focused on plant-fungal
symbiosis and genomics.}

\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------


\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{\thepage}

% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {July 19, 2023}
    {Bolívar Aponte Rolón~~~·~~~Curriculum Vitae}
  {\thepage~ of \pageref{LastPage}~}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Ph. D. candidate in Ecology and Evolutionary Biology}{Tulane University, Department of Ecology and Biology}{New Orleans, LA}{2018 - Present}{\begin{cvitems}
\item Committee members: Sunshine Van Bael, Ph.D. (adviser; dissertation chair), Kathleen Ferris, Ph.D.  (co-advisor), Keith Clay, Ph.D., \& P.Camilo Zalamea, Ph.D.
\end{cvitems}}
    \cventry{Master of Science, Natural Resources Management: Conservation Ecology,}{University of Michigan, School for the Environment and Sustainability}{Ann Arbor, MI}{2018}{}\vspace{-4.0mm}
    \cventry{Bachelor of Arts in Political Science,}{University of Puerto Rico}{San Juan, Puerto Rico}{2014}{\begin{cvitems}
\item Area of concentration: Political Theory, Magna Cum Laude
\end{cvitems}}
\end{cventries}

\hypertarget{peer-reviewed-publications}{%
\section{Peer Reviewed Publications}\label{peer-reviewed-publications}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-aponterolonTwoTreesEnvironmental2023}{}}%
\textbf{Aponte Rolón, B.}, \& Perfecto, I. (2023). Between Two Trees:
Environmental Effects of I. micheliana and A. latifolia on Leaf Litter
Ants in a Coffee Agroecosystem. \emph{Ecosphere}, \emph{14}(2), e4442.
\url{https://doi.org/10.1002/ecs2.4442}

\leavevmode\vadjust pre{\hypertarget{ref-schmittEvaluatingCommunityEffects2020a}{}}%
Schmitt, L., \textbf{Aponte Rolón, B.}, \& Perfecto, I. (2020).
Evaluating Community Effects of a Keystone Ant, Azteca sericeasur, on
Inga Micheliana Leaf Litter Decomposition in a Shaded Coffee
Agro-Ecosystem. \emph{Biotropica}, \emph{52}(6), 1253--1261.
\url{https://doi.org/10.1111/btp.12833}

\hypertarget{research-experience}{%
\section{Research Experience}\label{research-experience}}

\begin{cventries}
    \cventry{Master’s Thesis}{School for the Environment and Sustainability}{University of Michigan, Ann Arbor, MI}{January 2016 - April 2018}{\begin{cvitems}
\item “Impacts of quality of leaf-litter on ant assemblages in shade-grown coffee in the Soconusco region in Chiapas, Mexico”
\item PI, Ivette Perfecto, Ph. D.
\end{cvitems}}
    \cventry{Graduate Student Research Assistant}{School for the Environment and Sustainability}{University of Michigan, Ann Arbor, MI}{January 2016 - May 2016}{\begin{cvitems}
\item “Impacts of quality of leaf-litter on ant assemblages in shade-grown coffee in the Soconusco region in Chiapas, Mexico”
\item PI, Ivette Perfecto, Ph. D.
\end{cvitems}}
    \cventry{Undergraduate Research Assistant}{University of Puerto Rico}{Analytical Chemistry Division, Department of Chemistry, San Juan, PR}{January 2014 - May 2014}{\begin{cvitems}
\item PI, Liz Díaz, Ph. D.
\item Conducted GC-MS and QuECHERs methods in development of an analytical methodology for the detection of Hypoglycin A in Ackee Fruit (Blighia sapida).
\item Worked in the characterization of Ackee Fruit and applied the QuEChERS method to analyze analyte properties
\end{cvitems}}
    \cventry{Undergraduate Research Assistant}{University of Puerto Rico}{Center for Renewable Energy, Department of Chemistry, San Juan, PR}{June 2013 - July 2013}{\begin{cvitems}
\item PI, Liz Díaz, Ph. D.
\item Characterized and assessed marine algae as sources for biofuels, plastics, electrodes and bioindicators.
\item Conducted a simultaneous assay of pigments, carbohydrates, proteins and lipids of Tricleocarpa cylindrical.
\end{cvitems}}
    \cventry{Undergraduate Research Assistant}{Center for Landscape Conservation, Inc.}{San Juan, Puerto Rico}{July 2013 - July 2013}{\begin{cvitems}
\item PI, Federico Cintrón-Moscoso, Ph. D.
\item “Rapid Ethnographic Assessment in El Yunque: Understanding local visitors’ willingness and capacity to collaborate in the revision of EYNF’s Management Plan”
\end{cvitems}}
\end{cventries}

\hypertarget{grants-and-fellowships}{%
\section{Grants and Fellowships}\label{grants-and-fellowships}}

\begin{cventries}
    \cventry{Student Research Grant}{Department of Ecology and Evolutionary Biology}{Tulane University, New Orleans, LA.}{February  -  2022}{}\vspace{-4.0mm}
    \cventry{OGPS Fellowship}{Office of Graduate and Post-Doctoral Studies}{Tulane University, New Orleans, LA.}{November 2021 - May 2022}{\begin{cvitems}
\item Awarded \$3,000
\end{cvitems}}
    \cventry{Student Research Grant}{Department of Ecology and Evolutionary Biology}{Tulane University, New Orleans, LA.}{February  -  2021}{}\vspace{-4.0mm}
    \cventry{Student Research Grant}{Department of Ecology and Evolutionary Biology}{Tulane University, New Orleans, LA.}{February  -  2020}{}\vspace{-4.0mm}
    \cventry{Rackham International Research Award}{Rackham Graduate School}{University of Michigan, Ann Arbor, MI.}{April  -  2017}{\begin{cvitems}
\item Awarded   \$5,150
\end{cvitems}}
    \cventry{Rackham Conference Travel Grant}{Rackham Graduate School}{University of Michigan, Ann Arbor, MI.}{April  -  2017}{\begin{cvitems}
\item Awarded \$ 1,050
\end{cvitems}}
    \cventry{Rackham Master Fellowship}{Rackham Graduate School}{University of Michigan, Ann Arbor, MI.}{April  -  2015}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{awards-honors}{%
\section{Awards \& Honors}\label{awards-honors}}

\begin{cventries}
    \cventry{Summer Graduate Award}{The Connolly Alexander Institute for Data Science}{Tulane University, New Orleans, LA}{June 2023}{\begin{cvitems}
\item Awarded \$ 2,000
\end{cvitems}}
    \cventry{Travel Award}{Graduate Studies Student Association}{Tulane University, New Orleans, LA}{May 2023}{}\vspace{-4.0mm}
    \cventry{Dean’s Travel Award}{School of Science and Engineering}{Tulane University, New Orleans, LA}{May 2023}{}\vspace{-4.0mm}
    \cventry{Travel Award}{Graduate Studies Student Association}{Tulane University, New Orleans, LA}{May 2022}{}\vspace{-4.0mm}
    \cventry{Dean’s Travel Award}{School of Science and Engineering}{Tulane University, New Orleans, LA}{April 2022}{}\vspace{-4.0mm}
    \cventry{Jeffrey Lund Forest Ecology Award}{School for the Environment and Sustainability}{University of Michigan, Ann Arbor, MI}{April 2017}{\begin{cvitems}
\item Annual award for academic excellence, research capability and professional promise.
\end{cvitems}}
\end{cventries}

\hypertarget{conference-presentations-and-posters}{%
\section{Conference Presentations and
Posters}\label{conference-presentations-and-posters}}

\textbf{Aponte Rolón, B.} (2023 June). \emph{Oral Presentation}:
``Foliar fungal symbionts in sympatric yellow monkeyflowers along an
elevational gradient''. Evolution 2023, Albuquerque, NM.

\textbf{Aponte Rolón, B.} (2023 March). \emph{Poster}: ``The Influence
of host genotype and leaf trait plasticity on foliar fungal endophytes
of yellow monkeyflowers in Yosemite National Park, CA''. Collaborators:
Kathleen Ferris \& Sunshine Van Bael. Tulane Research, Innovation, and
Creativity Summit (TRICS), Jung Hotel Grand Hall, New Orleans, LA.

\textbf{Aponte Rolón, B.} (2022 July). \emph{Oral Presentation}:
``Interactions between functional leaf traits and foliar endophytes in
the defense against natural enemies of tropical trees'' (ID: 358). The
58th Meeting of the Association for Tropical Biology and Conservation
(ATBC 2022), Cartagena de Indias, Colombia.

\textbf{Aponte Rolón, B.} (2022 May). \emph{Poster}: ``The Influence of
host genotype and leaf trait plasticity on foliar fungal endophytes of
yellow monkeyflowers in Yosemite National Park, CA''. Collaborators:
Kathleen Ferris \& Sunshine Van Bael. Yosemite Symbiosis Workshop.
Wawona, CA, USA.

\textbf{Aponte Rolón, B.} (2020 July). \emph{Graphical Abstract}:
``Investigating trade-offs and complementarity between functional leaf
traits and foliar endophytic fungi in the defense against plant enemies
of tropical woody plants''. Collaborators: A. Elizabeth Arnold, and
Sunshine Van Bael. The Mycological Society of America's First Virtual
Meeting, MSA 2020: Mycology from the Cloud (virtual).

\textbf{Aponte Rolón, B.} (2019 May). \emph{Poster}: ``Leaf and Root
Endophytes of Mangroves in Southwestern Florida Everglades''.
Collaborators: Mareli Sánchez Juliá, Edward Castañeda, John Kominoski,
\& Sunshine Van Bael. Florida Coastal Everglades LTER All Scientists
Meeting. Fairchild Tropical Botanic Garden, Miami, Florida.

\textbf{Aponte Rolón, B.} (2017 October). \emph{Poster}: ``Quality of
leaf-litter and ant assemblages in shade-grown coffee in Chiapas,
Mexico'', Collaborator: Ivette Perfecto. Student Conference on
Conservation Science-New York (SCCS-NY), American Museum of Natural
History in New York City.

\textbf{Aponte Rolón, B.} (2017 July). \emph{Poster}: ``Impacts of
quality of leaf-litter on ant assemblages in shade-grown coffee in
Chiapas, Mexico'', Collaborator: Ivette Perfecto. 54th Annual Meeting of
the Association for Tropical Biology and Conservation, ``Ecological and
Social Dimensions of Tropical Biodiversity Conservation'', Merida,
Yucatan, Mexico.

\textbf{Aponte Rolón, B.} (2014 May). \emph{Poster}: ``El efecto del
Curcumin en la señalización celular de Artritis Psoriática'' {[}The
Effect of Curcumin on cell signaling of Psoriatic Arthritis{]}. (With
Carrero Feliciano, Heysel M.; Hall Laureano, Stephanie; Montes González,
Ingrid, PhD.) Annual poster presentation of the American Chemical
Society, Puerto Rico Chapter, University of Puerto Rico, Río Piedras
Campus, San Juan, Puerto Rico.

\hypertarget{seminars-workshops}{%
\section{Seminars \& Workshops}\label{seminars-workshops}}

\textbf{Delegate} (Aug.~Sept.~2014): \emph{``Encuentro latinoamericano y
caribeño: asamblea intermedia''}. {[}Intermediate Assembly of the
\emph{Consejo de Educación Popular de América Latina y el
Caribe-CEAAL}{]}. Quito, Ecuador.

\textbf{Delegate} (October 2013): \emph{``Rumbo a la asamblea
intermedia''}. Sponsored by the \emph{Consejo de Educación Popular de
América Latina y el Caribe-CEAAL}. Santo Domingo, Dominican Republic.

\textbf{Organizer} (August 2013): \emph{``Primer Encuentro Nacional de
Educadores(as) Populares de Puerto Rico''}. Sponsored by \emph{Consejo
de Educación Popular de América Latina y el Caribe-CEAAL}, Pontifical
Catholic University of Puerto Rico, Ponce, Puerto Rico.

\textbf{Workshop} (August 2013): \emph{``Educación Popular y Liberación
Nacional''} {[}Workshop on Popular Education and National Liberation{]}
Sponsored by \emph{La Nueva Escuela} at \emph{Primer Encuentro Nacional
de Educadores(as) Populares de Puerto Rico}. Pontifical Catholic
University of Puerto Rico, Ponce, Puerto Rico.

\textbf{Facilitator \& organizer} (March 2012): \emph{``Sexto Campamento
de Jóvenes: Educando para una nueva Patria''} {[}Summit on Popular
Education Critical Ideologies, Racism \& Xenophobia{]}. La Nueva
Escuela, Peñuelas, Puerto Rico.

\textbf{Organizer} (March 2012): \emph{``Debates y perspectivas en la
construcción de una reforma universitaria inclusiva''}. Sponsored by
Honors Program Student Association (AEPREH), University of Puerto Rico,
Río Piedras Campus. Social Sciences Faculty, University of Puerto Rico,
Río Piedras Campus, San Juan Puerto Rico.

\textbf{Round table} (July 2012): ``Puerto Rico: a brief historical
account''. Second International Summit \emph{``Entre las Crisis y Otros
Mundos Posibles''} of the Transnational Network of Other Knowledges.
Sponsored by \emph{Centro de Investigaciones y Estudios Superiores en
Antropología Social} (CIESAS), CIDECI Las Casas/ UNITIERRA-Chiapas, San
Cristóbal de las Casas, Chiapas, México.

\textbf{Workshop} (September 2010): \emph{``Taller de Educación
Popular''} {[}Workshop on Popular Education{]}. \emph{La Nueva Escuela}
at The University of Puerto Rico, Río Piedras Campus, San Juan, Puerto
Rico.

\textbf{Workshop} (May 2010): \emph{``Taller de Educación Popular y el
Movimiento Estudiantil''} {[}Workshop on Popular Education and the
Student Movement{]}. \emph{La Nueva Escuela} at The University of Puerto
Rico, Río Piedras Campus, San Juan, Puerto Rico.

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

Teaching Assistant

\hypertarget{tulane-university-2018-present}{%
\paragraph{Tulane University:
2018-Present}\label{tulane-university-2018-present}}

\begin{itemize}
\item
  Spring 2023 \textbar{} \textbf{Natural History of Louisiana - EBIO
  2330}. Dr.~Donata Henry, Department of Ecology and Evolutionary
  Biology.\\
\item
  Spring 2023 \textbar{} \textbf{Theory and Methods in Ecology and
  Evolutionary Biology - EBIO 2020}. Dr.~Donata Henry, Department of
  Ecology and Evolutionary Biology.\\
\item
  Fall 2022 \textbar{} \textbf{Entomology Lab -- EBIO 4430/4431}.
  Dr.~Dorothy Cheruiyot, Department of Ecology and Evolutionary
  Biology.\\
\item
  Spring 2022 \textbar{} \textbf{Insects and Human Interactions -- EBIO
  2210}. Dr.~Dorothy Cheruiyot, Department of Ecology and Evolutionary
  Biology.\\
\item
  Spring 2021 \textbar{} \textbf{Plants and Human Affairs with lab --
  EBIO 3180/3185}. Dr.~Keith Clay, Department of Ecology and
  Evolutionary Biology.\\
\item
  Fall 2020 \textbar{} \textbf{Entomology -- EBIO 4430/4431}.
  Dr.~Dorothy Cheruiyot, Department of Ecology and Evolutionary
  Biology.\\
\item
  Spring 2020 \textbar{} \textbf{Plant Biology and Adaptation with lab -
  EBIO 3590/3591}. Dr.~Dorothy Cheruiyot, Department of Ecology and
  Evolutionary Biology.\\
\item
  Spring 2019 \textbar{} \textbf{Entomology Lab -- EBIO 4430/4431}.
  Dr.~Dorothy Cheruiyot, Department of Ecology and Evolutionary
  Biology.\\
\item
  Fall 2018 \textbar{} \textbf{Diversity of Life - EBIO 1010}.
  Dr.~Donata Henry, Department of Ecology and Evolutionary Biology.\\
\end{itemize}

\hypertarget{guest-lectures}{%
\paragraph{Guest Lectures}\label{guest-lectures}}

\begin{itemize}
\item
  Fall 2021 \textbar{} \textbf{Tropical Biology -- EBIO 2110},
  Dr.~Renata Durães Ribeiro, Department of Ecology and Evolutionary
  Biology.\\
\item
  Fall 2021 \textbar{} \textbf{Entomology -- EBIO 4430/4431}.
  Dr.~Dorothy Cheruiyot, Department of Ecology and Evolutionary
  Biology.\\
\item
  Fall 2019 \textbar{} \textbf{Plants and Human Affairs -- EBIO
  3180/3185}. Dr.~Dorothy Cheruiyot, Department of Ecology and
  Evolutionary Biology.\\
\end{itemize}

\hypertarget{university-of-michigan-2016---2017}{%
\paragraph{University of Michigan: 2016 -
2017}\label{university-of-michigan-2016---2017}}

\begin{itemize}
\item
  Fall 2017 \textbar{} \textbf{NRE 509: Ecology: Concepts and
  Applications}. Dr.~Sheila K. Schueller, School for the Environment and
  Sustainability.\\
\item
  Fall 2016 \textbar{} \textbf{ENVIRON 270: Our Common Future}.
  Dr.~Ivette Perfecto, Program in The Environment, College of
  Literature, Science and the Arts.\\
\end{itemize}

\hypertarget{outreach}{%
\section{Outreach}\label{outreach}}

\begin{cventries}
    \cventry{FIRST Robotics Competition}{FIRST}{Bayou Regional}{March 2022}{\begin{cvitems}
\item Volunteer in robotics competition for high school students
\end{cvitems}}
    \cventry{Nature Talk}{Yosemite Conservancy}{Yosemite National Park}{May 2022}{\begin{cvitems}
\item Led public on nature walk and art activity to examine functional significance of leaf shapes.
\end{cvitems}}
    \cventry{EcoDia}{University of Michigan}{Finca Irlanda, Soconusco, Chiapas, Mexico}{June 2017}{\begin{cvitems}
\item Developed and executed a science communication day for the school.
\end{cvitems}}
\end{cventries}

\hypertarget{offices-and-other-experience}{%
\section{Offices and Other
Experience}\label{offices-and-other-experience}}

\begin{cventries}
    \cventry{Coordinator}{Tulanians Who Enjoy R Coding (TWERC)}{Tulane University, New Orleans, LA.}{January 2023 - Present }{}\vspace{-4.0mm}
    \cventry{Urban Agriculture Instructor}{AmeriCorps STATE}{Office of Community Alliances, Municipality of San Juan, San Juan, Puerto Rico}{December 2014 - June 2015}{}\vspace{-4.0mm}
    \cventry{Liason}{Consejo de Educación Popular de América Latina y el Caribe (CEAAL)}{Puerto Rico Committee}{November 2013 - June 2015}{}\vspace{-4.0mm}
    \cventry{Alternate Representative}{General Student Council Directive}{University of Puerto Rico's University Board}{August 2011 - May 2012}{}\vspace{-4.0mm}
    \cventry{President}{Honors Program Student Association (AEPREH)}{University of Puerto Rico, Río Piedras Campus}{August 2011 - May 2012}{}\vspace{-4.0mm}
    \cventry{Vice-President}{Honors Program Student Association (AEPREH)}{University of Puerto Rico, Río Piedras Campus}{August 2010 - May 2011}{}\vspace{-4.0mm}
    \cventry{Coordinator}{Social Sciences College Student Action Committee}{University of Puerto Rico, Río Piedras Campus}{August 2010 - May 2011}{}\vspace{-4.0mm}
    \cventry{Collaborator}{La Nueva Escuela}{San Juan, Puerto Rico}{September 2010 - May 2015}{}\vspace{-4.0mm}
\end{cventries}


\label{LastPage}~
\end{document}
