---
graphics: yes
name: Bolívar
surname: Aponte Rolón
headcolor: 414141
#qualifications: 
position: "Ph.D. candidate"
address: "3033 Chippewa St. | New Orleans, LA 70115"
phone: "+1-787-433-6970"
#www: 
email: "apontebolivar@gmail.com"
twitter: bolaponte
github: bolivaraponte
#linkedin: 
aboutme: |
  Ecologist.
date: '`r format(Sys.Date(), "%B %d, %Y")`'
csl: http://www.zotero.org/styles/apa
nocite: "@*"
header-includes:
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhf{}
  - \fancyhead[R]{\thepage}
output:
  vitae::awesomecv:
    page_total: true
    fig_caption: yes
    keep_tex: yes
    pandoc_args: ["--lua-filter=lua/strong.lua"]
     #- --lua-filter="lua/multiple-bibliographies.lua"
     # - --lua-filter="lua/highlight-author.lua"
      
engine: pdflatex
given-name-pattern: Bolívar
family-name-pattern: Aponte Rolón
#bibliography_packages: "bib/packages.bib"
---
```{r, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
opts_knit$set(output.dir = "C:/Users/boloq/Box/CV_Resume/CV/CVR_BAR")
opts_knit$get("tangle")

library(vitae)
library(tidyverse)
library(kableExtra)
library(readxl)
library(readr)
library(glue)
```

```{r, path}
path <- "C:/Users/boloq/Box/CV_Resume/CV/CVR_BAR/docs"
```

# Education

```{r, education}
read_excel(file.path(path, "education_bar.xlsx")) %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, 
                          when, 
                          with, 
                          where, 
                          why)
```



# Peer Reviewed Publications 

```{r}
bibliography_entries("bib/test4.bib")
```



# Research Experience

```{r, research}
read_excel(file.path(path, "research_bar.xlsx")) %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, 
                         when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}",.na = ""), 
                          with, 
                          where, 
                          why)
```

# Grants and Fellowships

```{r, grants}
read_excel(file.path(path, "grants.xlsx")) %>%
  # tidyr::fill(-why) %>%
  vitae::detailed_entries(what, 
                          when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}",.na = ""), 
                          with, 
                          where, 
                          why)
```

# Awards & Honors

```{r, awards}
read_excel(file.path(path, "awards.xlsx")) %>%
  # tidyr::fill(-why) %>%
  vitae::detailed_entries(what, 
                          when,
                          with, 
                          where, 
                          why)
```

# Conference Presentations and Posters

`r knitr::knit_child(file.path(path, "conferences.txt"))`

# Seminars & Workshops

`r knitr::knit_child(file.path(path, "seminars.txt"))`

# Teaching Experience

Teaching Assistant

#### Tulane University: 2018-Present 

  + Spring 2023 \| **Natural History of Louisiana - EBIO 2330**. Dr. Donata Henry, Department of Ecology and Evolutionary Biology.\

  + Spring 2023	\| **Theory and Methods in Ecology and Evolutionary Biology - EBIO 2020**. Dr. Donata Henry, Department of Ecology and Evolutionary Biology.\

   + Fall 2022 \| **Entomology Lab – EBIO 4430/4431**. Dr. Dorothy Cheruiyot,
Department of Ecology and Evolutionary Biology.\

  + Spring 2022 \| **Insects and Human Interactions – EBIO 2210**. Dr. Dorothy Cheruiyot, Department of Ecology and Evolutionary Biology.\

  + Spring 2021	\| **Plants and Human Affairs with lab – EBIO 3180/3185**. Dr. Keith Clay,
Department of Ecology and Evolutionary Biology.\

  + Fall 2020 \| **Entomology – EBIO 4430/4431**. Dr. Dorothy Cheruiyot,
Department of Ecology and Evolutionary Biology.\

  + Spring 2020	\| **Plant Biology and Adaptation with lab - EBIO 3590/3591**. Dr. Dorothy Cheruiyot, Department of Ecology and Evolutionary Biology.\

  + Spring 2019	\| **Entomology Lab – EBIO 4430/4431**. Dr. Dorothy Cheruiyot, Department of Ecology and Evolutionary Biology.\

  + Fall 2018	\| **Diversity of Life - EBIO 1010**. Dr. Donata Henry, Department of Ecology and Evolutionary Biology.\

#### Guest Lectures

  + Fall 2021 \| **Tropical Biology – EBIO 2110**, Dr. Renata Durães Ribeiro, Department of Ecology and Evolutionary Biology.\

  + Fall 2021 \| **Entomology – EBIO 4430/4431**. Dr. Dorothy Cheruiyot, Department of Ecology and Evolutionary Biology.\

  + Fall 2019	\| **Plants and Human Affairs – EBIO 3180/3185**. Dr. Dorothy Cheruiyot,
Department of Ecology and Evolutionary Biology.\


#### University of Michigan: 2016 - 2017

  + Fall 2017 \| **NRE 509: Ecology: Concepts and Applications**. Dr. Sheila K. Schueller, 
School for the Environment and Sustainability.\

  + Fall 2016	\| **ENVIRON 270: Our Common Future**. Dr. Ivette Perfecto,
Program in The Environment, College of Literature, Science and the Arts.\


# Packages

