%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Bolívar}{Aponte Rolón}

\position{Ph.D.~candidate}
\address{Department of Ecology and Evolutionary Biology \textbar{}
Tulane University, New Orleans, LA 70118}

\email{\href{mailto:apontebolivar@gmail.com}{\nolinkurl{apontebolivar@gmail.com}}}
\orcid{0000-0002-2544-4551}
\github{bolivaraponte}
\twitter{bolaponte}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}

\quote{I am a curiosity driven community ecologist focused on
plant-fungal symbiosis and genomics.}

\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------


\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{\thepage}
\usepackage{float}
\usepackage{multicol}
\usepackage{colortbl}
\arrayrulecolor{white}
\usepackage{hhline}
\definecolor{light-gray}{gray}{0.95}
\apptocmd{\tightlist}{\setlength{\itemsep}{2pt}}{}{}

% Pandoc CSL macros
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {February 28, 2024}
    {Bolívar Aponte Rolón~~~·~~~Curriculum Vitae}
  {\thepage~ of \pageref{LastPage}~}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\section{\texorpdfstring{\faIcon{graduation-cap}
Education}{ Education}}\label{education}

\begin{cventries}
    \cventry{Ph. D. candidate}{Tulane University (TU), Department of Ecology and Biology}{New Orleans, LA}{2018 - Present}{\begin{cvitems}
\item Committee members: Sunshine Van Bael, Ph.D. (advisor; dissertation chair), Kathleen Ferris, Ph.D.  (co-advisor), Keith Clay, Ph.D., \& P. Camilo Zalamea, Ph.D.
\end{cvitems}}
    \cventry{Master of Science, Natural Resources Management: Conservation Ecology}{University of Michigan (UM), School for the Environment and Sustainability}{Ann Arbor, MI}{2018}{}\vspace{-4.0mm}
    \cventry{Bachelor of Arts in Political Science,}{University of Puerto Rico (UPR)}{San Juan, Puerto Rico}{2014}{\begin{cvitems}
\item Area of concentration: Political Theory, Magna Cum Laude
\end{cvitems}}
\end{cventries}

\section{\texorpdfstring{\faIcon*{file} Peer-Reviewed
Publications}{ Peer-Reviewed Publications}}\label{peer-reviewed-publications}

\phantomsection\label{refs-9f84bd10e097ee738a8eb225e41dcd56}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-aponterolon2023a}
\textbf{Aponte Rolón, B.}, \& Perfecto, I. (2023). Between two trees:
Environmental effects of I. Micheliana and A. Latifolia on leaf litter
ants in a coffee agroecosystem. \emph{Ecosphere}, \emph{14}(2), e4442.
\url{https://doi.org/10.1002/ecs2.4442}

\bibitem[\citeproctext]{ref-schmitt2020}
Schmitt, L., \textbf{Aponte Rolón, B.}, \& Perfecto, I. (2020).
Evaluating community effects of a Keystone Ant,
\emph{Azteca sericeasur,} on \emph{Inga micheliana} leaf litter
decomposition in a shaded coffee agro-ecosystem. \emph{Biotropica},
\emph{52}(6), 1253--1261. \url{https://doi.org/10.1111/btp.12833}

\end{CSLReferences}

\section{\texorpdfstring{\faIcon{file} \emph{Other
Publications}}{ Other Publications}}\label{other-publications}

\phantomsection\label{refs-9c97e696cc6d6fa4babf22c263f6c715}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-aponterolon2023b}
\textbf{Aponte Rolón, B.} (2023). \emph{High-Molecular-Weight SPRI-aided
DNA extraction from Mimulus (Phrymaceae) leaf tissue.}
\url{https://doi.org/dx.doi.org/10.17504/protocols.io.bp2l6xn8rlqe/v2}

\end{CSLReferences}

\section{\texorpdfstring{\faIcon{microscope} Research
Experience}{ Research Experience}}\label{research-experience}

\begin{cventries}
    \cventry{Doctoral research}{Ecology and Evolutionary Biology}{Tulane University, New Orleans, LA}{August 2018 - Present }{\begin{cvitems}
\item “Leaf Functional Traits Influence on Foliar Endophytic Fungi and Their Effects on Plant’s Response to Herbivory and Pathogenicity In Tropical Trees”  (in progress)
\item “Foliar Endophytic Fungi in Yellow Monkeyflowers Along an Elevational Gradient in the Sierra Nevada, CA”  (in progress)
\item “Leaf Functional Trait Plasticity and Foliar Endophytic Fungi in Yellow Monkeyflowers: Linking Traits and Symbionts to Genes”  (in progress)
\item PI, Sunshine Van Bael Ph.D. \& Kathleen Ferris, Ph.D.
\end{cvitems}}
    \cventry{Master’s Thesis}{School for the Environment and Sustainability}{University of Michigan, Ann Arbor, MI}{January 2016 - April 2018}{\begin{cvitems}
\item “Impacts of quality of leaf-litter on ant assemblages in shade-grown coffee in the Soconusco region in Chiapas, Mexico”
\item PI, Ivette Perfecto, Ph. D.
\end{cvitems}}
    \cventry{Graduate Student Research Assistant}{School for the Environment and Sustainability}{University of Michigan, Ann Arbor, MI}{January 2016 - May 2016}{\begin{cvitems}
\item “Impacts of quality of leaf-litter on ant assemblages in shade-grown coffee in the Soconusco region in Chiapas, Mexico”
\item PI, Ivette Perfecto, Ph. D.
\end{cvitems}}
    \cventry{Undergraduate Research Assistant}{Department of Chemistry}{University of Puerto Rico, San Juan, PR}{January 2014 - May 2014}{\begin{cvitems}
\item Conducted GC-MS and QuECHERs methods in development of an analytical methodology for the detection of Hypoglycin A in Ackee Fruit (Blighia sapida).
\item Worked in the characterization of Ackee Fruit and applied the QuEChERS method to analyze analyte properties
\item PI, Liz Díaz, Ph. D.
\end{cvitems}}
    \cventry{Undergraduate Research Assistant}{Department of Chemistry}{University of Puerto Rico, San Juan, PR}{June 2013 - July 2013}{\begin{cvitems}
\item Characterized and assessed marine algae as sources for biofuels, plastics, electrodes and bioindicators.
\item Conducted a simultaneous assay of pigments, carbohydrates, proteins and lipids of Tricleocarpa cylindrica.
\item PI, Liz Díaz, Ph. D.
\end{cvitems}}
    \cventry{Undergraduate Research Assistant}{Center for Landscape Conservation, Inc.}{San Juan, Puerto Rico}{July 2013 - July 2013}{\begin{cvitems}
\item “Rapid Ethnographic Assessment in El Yunque: Understanding local visitors’ willingness and capacity to collaborate in the revision of EYNF’s Management Plan”
\item PI, Federico Cintrón-Moscoso, Ph. D.
\end{cvitems}}
\end{cventries}

\section{\texorpdfstring{\faIcon{medal} Grants and
Fellowships}{ Grants and Fellowships}}\label{grants-and-fellowships}

\begin{cventries}
    \cventry{Department of Ecology and Evolutionary Biology}{Student Research Grant}{Tulane University, New Orleans, LA.}{February 2020 - 2021 ,2022}{}\vspace{-4.0mm}
    \cventry{Office of Graduate and Post-Doctoral Studies}{OGPS Fellowship}{Tulane University, New Orleans, LA.}{November 2021 - May 2022}{}\vspace{-4.0mm}
    \cventry{Rackham Graduate School}{Rackham International Research Award}{University of Michigan, Ann Arbor, MI.}{April  -  2017}{}\vspace{-4.0mm}
    \cventry{Rackham Graduate School}{Rackham Conference Travel Grant}{University of Michigan, Ann Arbor, MI.}{April  -  2017}{}\vspace{-4.0mm}
    \cventry{Rackham Graduate School}{Rackham Master Fellowship}{University of Michigan, Ann Arbor, MI.}{April  -  2015}{}\vspace{-4.0mm}
\end{cventries}

\section{\texorpdfstring{\faIcon{award} Awards \&
Honors}{ Awards \& Honors}}\label{awards-honors}

\begin{cventries}
    \cventry{Summer Graduate Award}{The Connolly Alexander Institute for Data Science}{Tulane University, New Orleans, LA}{June 2023}{}\vspace{-4.0mm}
    \cventry{Travel Award}{Graduate Studies Student Association}{Tulane University, New Orleans, LA}{May 2023}{}\vspace{-4.0mm}
    \cventry{Dean’s Travel Award}{School of Science and Engineering}{Tulane University, New Orleans, LA}{May 2023}{}\vspace{-4.0mm}
    \cventry{Travel Award}{Graduate Studies Student Association}{Tulane University, New Orleans, LA}{May 2022}{}\vspace{-4.0mm}
    \cventry{Dean’s Travel Award}{School of Science and Engineering}{Tulane University, New Orleans, LA}{April 2022}{}\vspace{-4.0mm}
    \cventry{Jeffrey Lund Forest Ecology Award}{School for the Environment and Sustainability}{University of Michigan, Ann Arbor, MI}{April 2017}{\begin{cvitems}
\item Annual award for academic excellence, research capability and professional promise.
\end{cvitems}}
\end{cventries}

\section{\texorpdfstring{\faIcon{chalkboard-teacher} Conference
Presentations and
Posters}{ Conference Presentations and Posters}}\label{conference-presentations-and-posters}

\textbf{Aponte Rolón, B.} (2023 June). \emph{Oral Presentation}:
``Foliar fungal symbionts in sympatric yellow monkeyflowers along an
elevational gradient''. Evolution 2023, Albuquerque, NM.

\textbf{Aponte Rolón, B.} (2023 March). \emph{Poster}: ``The Influence
of host genotype and leaf trait plasticity on foliar fungal endophytes
of yellow monkeyflowers in Yosemite National Park, CA''. Collaborators:
Kathleen Ferris \& Sunshine Van Bael. Tulane Research, Innovation, and
Creativity Summit (TRICS), Jung Hotel Grand Hall, New Orleans, LA.

\textbf{Aponte Rolón, B.} (2022 July). \emph{Oral Presentation}:
``Interactions between functional leaf traits and foliar endophytes in
the defense against natural enemies of tropical trees'' (ID: 358). The
58th Meeting of the Association for Tropical Biology and Conservation
(ATBC 2022), Cartagena de Indias, Colombia.

\textbf{Aponte Rolón, B.} (2022 May). \emph{Poster}: ``The Influence of
host genotype and leaf trait plasticity on foliar fungal endophytes of
yellow monkeyflowers in Yosemite National Park, CA''. Collaborators:
Kathleen Ferris \& Sunshine Van Bael. Yosemite Symbiosis Workshop.
Wawona, CA, USA.

\textbf{Aponte Rolón, B.} (2020 July). \emph{Graphical Abstract}:
``Investigating trade-offs and complementarity between functional leaf
traits and foliar endophytic fungi in the defense against plant enemies
of tropical woody plants''. Collaborators: A. Elizabeth Arnold, and
Sunshine Van Bael. The Mycological Society of America's First Virtual
Meeting, MSA 2020: Mycology from the Cloud (virtual).

\textbf{Aponte Rolón, B.} (2019 May). \emph{Poster}: ``Leaf and Root
Endophytes of Mangroves in Southwestern Florida Everglades''.
Collaborators: Mareli Sánchez Juliá, Edward Castañeda, John Kominoski,
\& Sunshine Van Bael. Florida Coastal Everglades LTER All Scientists
Meeting. Fairchild Tropical Botanic Garden, Miami, Florida.

\textbf{Aponte Rolón, B.} (2017 October). \emph{Poster}: ``Quality of
leaf-litter and ant assemblages in shade-grown coffee in Chiapas,
Mexico'', Collaborator: Ivette Perfecto. Student Conference on
Conservation Science-New York (SCCS-NY), American Museum of Natural
History in New York City.

\textbf{Aponte Rolón, B.} (2017 July). \emph{Poster}: ``Impacts of
quality of leaf-litter on ant assemblages in shade-grown coffee in
Chiapas, Mexico'', Collaborator: Ivette Perfecto. 54th Annual Meeting of
the Association for Tropical Biology and Conservation, ``Ecological and
Social Dimensions of Tropical Biodiversity Conservation'', Merida,
Yucatan, Mexico.

\textbf{Aponte Rolón, B.} (2014 May). \emph{Poster}: ``El efecto del
Curcumin en la señalización celular de Artritis Psoriática'' {[}The
Effect of Curcumin on cell signaling of Psoriatic Arthritis{]}. (With
Carrero Feliciano, Heysel M.; Hall Laureano, Stephanie; Montes González,
Ingrid, PhD.) Annual poster presentation of the American Chemical
Society, Puerto Rico Chapter, University of Puerto Rico, Río Piedras
Campus, San Juan, Puerto Rico.

\section{\texorpdfstring{\faIcon{comments} Seminars \&
Workshops}{ Seminars \& Workshops}}\label{seminars-workshops}

\textbf{Delegate} (Aug.~Sept.~2014): \emph{``Encuentro latinoamericano y
caribeño: asamblea intermedia''}. {[}Intermediate Assembly of the
\emph{Consejo de Educación Popular de América Latina y el
Caribe-CEAAL}{]}. Quito, Ecuador.

\textbf{Delegate} (October 2013): \emph{``Rumbo a la asamblea
intermedia''}. Sponsored by the \emph{Consejo de Educación Popular de
América Latina y el Caribe-CEAAL}. Santo Domingo, Dominican Republic.

\textbf{Organizer} (August 2013): \emph{``Primer Encuentro Nacional de
Educadores(as) Populares de Puerto Rico''}. Sponsored by \emph{Consejo
de Educación Popular de América Latina y el Caribe-CEAAL}, Pontifical
Catholic University of Puerto Rico, Ponce, Puerto Rico.

\textbf{Workshop Developer} (August 2013): \emph{``Educación Popular y
Liberación Nacional''} {[}Workshop on Popular Education and National
Liberation{]} Sponsored by \emph{La Nueva Escuela} at \emph{Primer
Encuentro Nacional de Educadores(as) Populares de Puerto Rico}.
Pontifical Catholic University of Puerto Rico, Ponce, Puerto Rico.

\textbf{Facilitator \& organizer} (March 2012): \emph{``Sexto Campamento
de Jóvenes: Educando para una nueva Patria''} {[}Summit on Popular
Education Critical Ideologies, Racism \& Xenophobia{]}. La Nueva
Escuela, Peñuelas, Puerto Rico.

\textbf{Organizer} (March 2012): \emph{``Debates y perspectivas en la
construcción de una reforma universitaria inclusiva''}. Sponsored by
Honors Program Student Association (AEPREH), University of Puerto Rico,
Río Piedras Campus. Social Sciences Faculty, University of Puerto Rico,
Río Piedras Campus, San Juan Puerto Rico.

\textbf{Round table} (July 2012): ``Puerto Rico: a brief historical
account''. Second International Summit \emph{``Entre las Crisis y Otros
Mundos Posibles''} of the Transnational Network of Other Knowledges.
Sponsored by \emph{Centro de Investigaciones y Estudios Superiores en
Antropología Social} (CIESAS), CIDECI Las Casas/ UNITIERRA-Chiapas, San
Cristóbal de las Casas, Chiapas, México.

\textbf{Workshop Developer} (September 2010): \emph{``Taller de
Educación Popular''} {[}Workshop on Popular Education{]}. \emph{La Nueva
Escuela} at The University of Puerto Rico, Río Piedras Campus, San Juan,
Puerto Rico.

\textbf{Workshop Developer} (May 2010): \emph{``Taller de Educación
Popular y el Movimiento Estudiantil''} {[}Workshop on Popular Education
and the Student Movement{]}. \emph{La Nueva Escuela} at The University
of Puerto Rico, Río Piedras Campus, San Juan, Puerto Rico.

\section{\texorpdfstring{\faIcon{chalkboard} Teaching
Experience}{ Teaching Experience}}\label{teaching-experience}

\paragraph{\texorpdfstring{Tulane University: 2018-Present\\
}{Tulane University: 2018-Present }}\label{tulane-university-2018-present}

Instructor

\begin{itemize}
\item
  October 2023 \textbar{} \emph{Introduction to Version Control with Git
  and GitHub}. Developed by \textbf{B. Aponte Rolón} for the
  Howard-Tilton Memorial Library, Tulane University, New Orleans LA.
\item
  October 2023 \textbar{} \emph{Introduction to Data Visualization in
  R}. Developed by \textbf{B. Aponte Rolón} for the Howard-Tilton
  Memorial Library, Tulane University, New Orleans LA.
\item
  October 2023 \textbar{} \emph{Introduction to R, Part 1}. Developed by
  Mike Ellis for the Howard-Tilton Memorial Library, Tulane University,
  New Orleans LA.
\end{itemize}

Teaching Assistant

\begin{itemize}
\item
  Summer 2023 \textbar{} \textbf{Tropical Field Biology - EBIO 3780}.
  Dr.~Sunshine Van Bael, Department of Ecology and Evolutionary Biology.
\item
  Spring 2023 \textbar{} \textbf{Natural History of Louisiana - EBIO
  2330}. Dr. Donata Henry, Department of Ecology and Evolutionary
  Biology.
\item
  Spring 2023 \textbar{} \textbf{Theory and Methods in Ecology and
  Evolutionary Biology - EBIO 2020}. Dr.~Donata Henry, Department of
  Ecology and Evolutionary Biology.
\item
  Fall 2022 \textbar{} \textbf{Entomology -- EBIO 4430/4431}.
  Dr.~Jelagat Cheruiyot, Department of Ecology and Evolutionary Biology.
\item
  Spring 2022 \textbar{} \textbf{Insects and Human Interactions -- EBIO
  2210}. Dr. Jelagat Cheruiyot, Department of Ecology and Evolutionary
  Biology.
\item
  Fall 2021 \textbar{} \textbf{Entomology -- EBIO 4430/4431}.
  Dr.~Jelagat Cheruiyot, Department of Ecology and Evolutionary Biology.
\item
  Spring 2021 \textbar{} \textbf{Plants and Human Affairs -- EBIO
  3180/3185}. Dr.~Keith Clay, Department of Ecology and Evolutionary
  Biology.
\item
  Fall 2020 \textbar{} \textbf{Entomology -- EBIO 4430/4431}.
  Dr.~Jelagat Cheruiyot, Department of Ecology and Evolutionary Biology.
\item
  Spring 2020 \textbar{} \textbf{Plant Biology and Adaptation - EBIO
  3590/3591}. Dr.~Jelagat Cheruiyot, Department of Ecology and
  Evolutionary Biology.
\item
  Fall 2019 \textbar{} \textbf{Plants and Human Affairs -- EBIO
  3180/3185}. Dr. Jelagat Cheruiyot, Department of Ecology and
  Evolutionary Biology.
\item
  Spring 2019 \textbar{} \textbf{Entomology -- EBIO 4430/4431}.
  Dr.~Jelagat Cheruiyot, Department of Ecology and Evolutionary Biology.
\item
  Fall 2018 \textbar{} \textbf{Diversity of Life - EBIO 1010}.
  Dr.~Donata Henry, Department of Ecology and Evolutionary Biology.
\end{itemize}

\paragraph{Guest Lectures}\label{guest-lectures}

\begin{itemize}
\item
  Summer 2023 \textbar{} \textbf{Tropical Field Biology - EBIO 3780},
  Dr.~Sunshine Van Bael, Department of Ecology and Evolutionary Biology.
\item
  Fall 2021 \textbar{} \textbf{Tropical Biology -- EBIO 2110},
  Dr.~Renata Durães Ribeiro, Department of Ecology and Evolutionary
  Biology.
\item
  Fall 2021 \textbar{} \textbf{Entomology -- EBIO 4430/4431}.
  Dr.~Jelagat Cheruiyot, Department of Ecology and Evolutionary Biology.
\item
  Fall 2019 \textbar{} \textbf{Plants and Human Affairs -- EBIO
  3180/3185}. Dr. Jelagat Cheruiyot, Department of Ecology and
  Evolutionary Biology.
\end{itemize}

\paragraph{University of Michigan: 2016 -
2017}\label{university-of-michigan-2016---2017}

\begin{itemize}
\item
  Fall 2017 \textbar{} \textbf{NRE 509: Ecology: Concepts and
  Applications}. Dr. Sheila K. Schueller, School for the Environment and
  Sustainability.
\item
  Fall 2016 \textbar{} \textbf{ENVIRON 270: Our Common Future}.
  Dr.~Ivette Perfecto, Program in The Environment, College of
  Literature, Science and the Arts.\\
\end{itemize}

\section{\texorpdfstring{\faIcon[regular]{comments}
Outreach}{ Outreach}}\label{outreach}

\begin{cventries}
    \cventry{FIRST Robotics Competition}{FIRST}{Bayou Regional}{March 2022}{\begin{cvitems}
\item Volunteer in robotics competition for high school students
\end{cvitems}}
    \cventry{Nature Talk}{Yosemite Conservancy}{Yosemite National Park}{May 2022}{\begin{cvitems}
\item Led public on nature walk and art activity to examine functional significance of leaf shapes.
\end{cvitems}}
    \cventry{EcoDia}{University of Michigan}{Finca Irlanda, Soconusco, Chiapas, Mexico}{June 2017}{\begin{cvitems}
\item Developed and executed a science communication day for the school.
\end{cvitems}}
\end{cventries}

\section{\texorpdfstring{\faIcon{users-cog} Offices and Other
Experience}{ Offices and Other Experience}}\label{offices-and-other-experience}

\begin{cventries}
    \cventry{Product Developer}{Connolly Alexander Institute for Data Science}{}{January 2024 - Present }{}\vspace{-4.0mm}
    \cventry{Instructor}{Howard-Tilton Memorial Library,}{}{September 2023 - December 2023}{}\vspace{-4.0mm}
    \cventry{Coordinator}{Tulanians Who Enjoy R Coding (TWERC)}{}{January 2023 - January 2024}{}\vspace{-4.0mm}
    \cventry{Urban Agriculture Instructor}{AmeriCorps STATE}{}{December 2014 - June 2015}{}\vspace{-4.0mm}
    \cventry{Liason}{Consejo de Educación Popular de América Latina y el Caribe (CEAAL)}{}{November 2013 - June 2015}{}\vspace{-4.0mm}
    \cventry{Alternate Representative}{General Student Council Directive}{}{August 2011 - May 2012}{}\vspace{-4.0mm}
    \cventry{President}{Honors Program Student Association (AEPREH)}{}{August 2011 - May 2012}{}\vspace{-4.0mm}
    \cventry{Vice-President}{Honors Program Student Association (AEPREH)}{}{August 2010 - May 2011}{}\vspace{-4.0mm}
    \cventry{Coordinator}{Social Sciences College Student Action Committee}{}{August 2010 - May 2011}{}\vspace{-4.0mm}
    \cventry{Collaborator}{La Nueva Escuela}{}{September 2010 - May 2015}{}\vspace{-4.0mm}
\end{cventries}

\section{\texorpdfstring{\faIcon{users}
Memberships}{ Memberships}}\label{memberships}

\textbf{ATBC} \textbar{} Association for Tropical Biology and
Conservation

\textbf{ESA} \textbar{} Ecological Society of America

\textbf{SSE} \textbar{} Society for the Study of Evolution

\section{\texorpdfstring{\faIcon{brain} Skills}{ Skills}}\label{skills}

\smallskip

\section{\texorpdfstring{\faIcon{cogs}
Technical}{ Technical}}\label{technical}

\begin{table}[H]
\centering\begingroup\fontsize{10}{12}\selectfont

\begin{tabular}{>{\centering\arraybackslash}p{3.75cm}>{\centering\arraybackslash}p{3.75cm}}
\toprule
\begingroup\fontsize{12}{14}\selectfont \textcolor[HTML]{414141}{\textbf{Skill}}\endgroup & \begingroup\fontsize{12}{14}\selectfont \textcolor[HTML]{414141}{\textbf{Proficiency}}\endgroup\\
\midrule
\textcolor[HTML]{7f7f9f}{R} & \textcolor[HTML]{7f7f9f}{Advanced}\\
\textcolor[HTML]{7f7f9f}{Bash} & \textcolor[HTML]{7f7f9f}{Intermediate}\\
\textcolor[HTML]{7f7f9f}{Python} & \textcolor[HTML]{7f7f9f}{Beginner}\\
\textcolor[HTML]{7f7f9f}{LaTex} & \textcolor[HTML]{7f7f9f}{Beginner}\\
\textcolor[HTML]{7f7f9f}{Fusion 360} & \textcolor[HTML]{7f7f9f}{Intermediate}\\
\addlinespace
\textcolor[HTML]{7f7f9f}{Inkscape} & \textcolor[HTML]{7f7f9f}{Intermediate}\\
\textcolor[HTML]{7f7f9f}{Git} & \textcolor[HTML]{7f7f9f}{Intermediate}\\
\textcolor[HTML]{7f7f9f}{Markdown} & \textcolor[HTML]{7f7f9f}{Intermediate}\\
\bottomrule
\end{tabular}
\endgroup{}
\end{table}

\section{\texorpdfstring{\faIcon{language}
Languages}{ Languages}}\label{languages}

\begin{table}[H]
\centering\begingroup\fontsize{10}{12}\selectfont

\begin{tabular}{>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}}
\toprule
\begingroup\fontsize{12}{14}\selectfont \textcolor[HTML]{414141}{\textbf{Skill}}\endgroup & \begingroup\fontsize{12}{14}\selectfont \textcolor[HTML]{414141}{\textbf{Spanish}}\endgroup & \begingroup\fontsize{12}{14}\selectfont \textcolor[HTML]{414141}{\textbf{English}}\endgroup & \begingroup\fontsize{12}{14}\selectfont \textcolor[HTML]{414141}{\textbf{Portuguese}}\endgroup\\
\midrule
Reading & \textcolor[HTML]{7f7f9f}{Native} & \textcolor[HTML]{7f7f9f}{Advanced} & \textcolor[HTML]{7f7f9f}{Intermediate}\\
Writing & \textcolor[HTML]{7f7f9f}{Native} & \textcolor[HTML]{7f7f9f}{Advanced} & \textcolor[HTML]{7f7f9f}{Intermediate}\\
Listening & \textcolor[HTML]{7f7f9f}{Native} & \textcolor[HTML]{7f7f9f}{Advanced} & \textcolor[HTML]{7f7f9f}{Intermediate}\\
Speaking & \textcolor[HTML]{7f7f9f}{Native} & \textcolor[HTML]{7f7f9f}{Advanced} & \textcolor[HTML]{7f7f9f}{Intermediate}\\
\bottomrule
\end{tabular}
\endgroup{}
\end{table}


\label{LastPage}~
\end{document}
