---
graphics: yes
name: Bolívar
surname: Aponte Rolón
headcolor: 414141
#profilepic: "C:/Users/boloq/Box/CV_Resume/Bolivar Aponte_Headshots_2022/Bolivar Aponte-pbc-1961.jpg"
#qualifications: 
position: "Ph.D. candidate"
address: "Department of Ecology and Evolutionary Biology | Tulane University, New Orleans, LA 70118"
phone: "+1-787-433-6970"
#www: 
email: apontebolivar@gmail.com
twitter: bolaponte
github: bolivaraponte
orcid: 0000-0002-2544-4551
#linkedin: 
aboutme: I am a curiosity driven community ecologist focused on plant-fungal symbiosis and genomics.
date: '`r format(Sys.Date(), "%B %d, %Y")`'
csl: "csl/apa6-cv.csl"
nocite: "@*"
header-includes:
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhf{}
  - \fancyhead[R]{\thepage}
  - \usepackage{float}
  - \usepackage{multicol}
  - \usepackage{colortbl}
  - \arrayrulecolor{white}
  - \usepackage{hhline}
  - \definecolor{light-gray}{gray}{0.95}
  - \apptocmd{\tightlist}{\setlength{\itemsep}{2pt}}{}{}
output:
   
  vitae::awesomecv:
     #- --lua-filter="lua/highlight-author.lua"
    page_total: true
    fig_caption: yes
    keep_tex: yes
    pandoc_args: 
     - --lua-filter="lua/strong_sur.lua"
     - --lua-filter="lua/emph.lua"
engine: xelatex
#bibliography_packages: "bib/packages.bib"
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
opts_knit$set(output.dir = "C:/Users/boloq/Box/CV_Resume/CV/CVR_BAR")
#opts_knit$set(output.dir = "/home/baponte/Box/CV_Resume/CV/CVR_BAR")
opts_knit$get("tangle")

library(vitae)
library(tidyverse)
library(kableExtra)
library(readxl)
library(readr)
library(glue)
library(ggrepel)
library(emojifont)
library(fontawesome)
#library(huxtable)
library(gridExtra)
library(ggplot2)
```

```{r, path}
path <- "C:/Users/boloq/Box/CV_Resume/CV/CVR_BAR"
#path <- "/home/baponte/Box/CV_Resume/CV/CVR_BAR"
```

\faIcon{graduation-cap} Education
===============================

```{r, education}
read_excel(file.path(path, "docs/education_bar.xlsx")) %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, 
                          when, 
                          with, 
                          where, 
                          why)
```

\faIcon{file} Peer-Reviewed Publications
===============================

```{r}
bibliography_entries("bib/bar_publications.bib")
```

\faIcon{file} *Other Publications*
===============================
```{r}
bibliography_entries("bib/nonpeer_publications.bib")
```

\faIcon{microscope} Research Experience
===============================

```{r, research}
read_excel(file.path(path, "docs/research_bar.xlsx")) %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, 
                         when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}",.na = ""), 
                          with, 
                          where, 
                          why)
```

\faIcon{medal} Grants and Fellowships
===============================

```{r, grants}
read_excel(file.path(path, "docs/grants.xlsx")) %>%
  # tidyr::fill(-why) %>%
  vitae::detailed_entries(with,
                          what, 
                          when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}",.na = ""), 
                          where, 
                          why)
```

\faIcon{award} Awards & Honors
===============================

```{r, awards}
read_excel(file.path(path, "docs/awards.xlsx")) %>%
  # tidyr::fill(-why) %>%
  vitae::detailed_entries(what,
                          when,
                          with,
                          where, 
                          why)
```

\faIcon{chalkboard-teacher} Conference Presentations and Posters
===============================

`r knitr::knit_child(file.path(path, "docs/conferences.txt"))`

\faIcon{comments} Seminars & Workshops
===============================

`r knitr::knit_child(file.path(path, "docs/seminars.txt"))`

\faIcon{chalkboard} Teaching Experience
===============================

Teaching Assistant

#### Tulane University: 2018-Present

-   Summer 2023 \| **Tropical Field Biology - EBIO 3780**. Dr. Sunshine
    Van Bael, Department of Ecology and Evolutionary Biology.

-   Spring 2023 \| **Natural History of Louisiana - EBIO 2330**. Dr.
    Donata Henry, Department of Ecology and Evolutionary Biology.

-   Spring 2023 \| **Theory and Methods in Ecology and Evolutionary
    Biology - EBIO 2020**. Dr. Donata Henry, Department of Ecology and
    Evolutionary Biology.

-   Fall 2022 \| **Entomology -- EBIO 4430/4431**. Dr. Jelagat
    Cheruiyot, Department of Ecology and Evolutionary Biology.

-   Spring 2022 \| **Insects and Human Interactions -- EBIO 2210**. Dr.
    Jelagat Cheruiyot, Department of Ecology and Evolutionary Biology.

-   Fall 2021 \| **Entomology -- EBIO 4430/4431**. Dr. Jelagat
    Cheruiyot, Department of Ecology and Evolutionary Biology.

-   Spring 2021 \| **Plants and Human Affairs -- EBIO    3180/3185**. Dr. Keith Clay, Department of Ecology and Evolutionary
    Biology.

-   Fall 2020 \| **Entomology -- EBIO 4430/4431**. Dr. Jelagat
    Cheruiyot, Department of Ecology and Evolutionary Biology.

-   Spring 2020 \| **Plant Biology and Adaptation - EBIO 3590/3591**. Dr. Jelagat Cheruiyot, Department of Ecology and
    Evolutionary Biology.

-   Fall 2019 \| **Plants and Human Affairs -- EBIO 3180/3185**. Dr.
    Jelagat Cheruiyot, Department of Ecology and Evolutionary Biology.

-   Spring 2019 \| **Entomology -- EBIO 4430/4431**. Dr. Jelagat
    Cheruiyot, Department of Ecology and Evolutionary Biology.

-   Fall 2018 \| **Diversity of Life - EBIO 1010**. Dr. Donata Henry,
    Department of Ecology and Evolutionary Biology.

#### Guest Lectures

-   Summer 2023 \| **Tropical Field Biology - EBIO 3780**, Dr. Sunshine
    Van Bael, Department of Ecology and Evolutionary Biology.

-   Fall 2021 \| **Tropical Biology -- EBIO 2110**, Dr. Renata Durães
    Ribeiro, Department of Ecology and Evolutionary Biology.

-   Fall 2021 \| **Entomology -- EBIO 4430/4431**. Dr. Jelagat
    Cheruiyot, Department of Ecology and Evolutionary Biology.

-   Fall 2019 \| **Plants and Human Affairs -- EBIO 3180/3185**. Dr.
    Jelagat Cheruiyot, Department of Ecology and Evolutionary Biology.

#### University of Michigan: 2016 - 2017

-   Fall 2017 \| **NRE 509: Ecology: Concepts and Applications**. Dr.
    Sheila K. Schueller, School for the Environment and Sustainability.

-   Fall 2016 \| **ENVIRON 270: Our Common Future**. Dr. Ivette
    Perfecto, Program in The Environment, College of Literature, Science
    and the Arts.\

\faIcon[regular]{comments} Outreach
===============================

```{r}
read_excel(file.path(path, "docs/outreach.xlsx")) %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, 
                         when = glue::glue("{endMonth} {endYear}",.na = ""), 
                          with, 
                          where, 
                          why)
```

\faIcon{users-cog} Offices and Other Experience
===============================

```{r}
read_excel(file.path(path, "docs/offices.xlsx")) %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, 
                         when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}",.na = ""), 
                          with, 
                          #where, 
                          why)

```

\faIcon{users} Memberships
===============================

**ATBC** \| Association for Tropical Biology and Conservation

**ESA** \| Ecological Society of America

**SSE** \| Society for the Study of Evolution

\faIcon{brain} Skills
===============================

\smallskip

\faIcon{language} Languages
===============================

```{r langforeign, results='markup'}
data.frame(
  Skill = c("Reading", "Writing", "Listening","Speaking"),
  Spanish = cell_spec(c(rep("Native", 4)), 'latex', color = '#7f7f9f'),
  English = cell_spec(c(rep("Advanced", 4)), 'latex', color = '#7f7f9f'),
  Portuguese = cell_spec(c(rep("Intermediate", 4)), 'latex', color = '#7f7f9f')
 )|>
   kable(booktabs = T, align = 'c', escape = F, format = "latex") |>
   kable_styling(full_width = F, font_size = 10, latex_options = "HOLD_position") |>
  row_spec(0, bold = T, color = "#414141")|>
   column_spec(column = 1:4, width = '4.5cm')
```

\faIcon{cogs} Technical skills

```{r techtable, results='markup'}

# lang= matrix(c(7, 5, 3), ncol=1, byrow=FALSE)
# colnames(lang) <- c("Proficiency")
# rownames <- c("R", "Bash", "Python")
# lang <- tibble::rownames_to_column(lang, "Prgramming language")
# 
# lang <- as_tibble(lang)
# lang
# lang <- c("R", "Bash", "Python")
# rate <- c(7, 5, 3)
#table <- tibbble(cbind(rate, lang))
#
tribble(
   ~`Coding Languages`, ~Software, ~Other,
  "R -- Bash",
  "Fusion 360 -- Inkscape",
  "Git -- Markdown -- LaTex"
) |>
kable(booktabs = T, align = 'c', escape = F, format = "latex") |>
kable_styling(full_width = F, font_size = 10, latex_options = "HOLD_position") |>
row_spec(0, bold = T, color = "#414141") |>
row_spec(1, bold = F, color = "#7f7f9f") |>
column_spec(column = 1:3, width = '4.75cm')
```
